\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Commands for resume formatting
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=-]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge NATHNAEL T. AGAFARI} \\ \vspace{1pt}
    \small +251-996904151 $|$ \href{mailto:hellonathnael@gmail.com}{hellonathnael@gmail.com} $|$ \href{https://linkedin.com/in/nathnaeltk}{linkedin.com/in/nathnaeltk}
\end{center}

%-----------HONORS-----------
\section{Honors, Scholarships, and Awards}
\resumeSubHeadingListStart
\resumeItem{ A2SV - Africa to Silicon Valley Program, Addis Ababa, Ethiopia.}
\resumeItem{ Full Stack Software Engineering (African Leadership University – ALX).}
\resumeItem{ Pan Africa Youth Leadership Program PAYLP, Portland, Oregon, USA (U.S. Department of State).}
\resumeItem{ PAYLP All Stars Leadership Program, Huntsville, Alabama, USA (U.S. Department of State).}
\resumeItem{ Young African Leaders Initiative Regional Leadership Conference YALI RLC EA, Nairobi, Kenya.}
\resumeItem{ Aspire Institute Leadership Program, Harvard University, USA.}
\resumeItem{ United Nations African Youth Delegate Program.}

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Outreach Coordinator, UWC UMOJA Short Course}{Dec 2023 -- Present}{Moshi, Kilimanjaro, Tanzania}{}
\resumeItemListStart
\resumeItem{ Developed and implemented external outreach strategy for fundraising.}
\resumeItem{ Strategically managed UMOJA online engagement through social media accounts and website.}
\resumeItemListEnd

\resumeSubheading{Full Stack Web Developer, Mado Technology Solutions PLC}{Jan 2023 -- Present}{Addis Ababa, Ethiopia}{}
\resumeItemListStart
\resumeItem{ Full stack web development, team leadership, API development, front/back-end development, database design, deployment, and dev-ops.}
\resumeItemListEnd

\resumeSubheading{Software Engineer Fellow, Africa to Silicon Valley A2SV}{June 2023 -- July 2023}{Addis Ababa, Ethiopia}{}
\resumeItemListStart
\resumeItem{ Gained expertise in competitive programming, data structures, and algorithms.}
\resumeItem{ Participated in project development with Silicon Valley mentors.}
\resumeItemListEnd

\resumeSubheading{Project Director, The Ignite Initiative}{May 2023 -- Present}{Haramaya University, Ethiopia}{}
\resumeItemListStart
\resumeItem{ Led STEM education improvement programs for middle/high school students.}
\resumeItem{ Designed training materials and managed outreach, social media, and web presence.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Competitive Programming (Data Structures and Algorithms)}{Feb 2024}{Africa to Silicon Valley}{Addis Ababa, Ethiopia}
\resumeSubheading{ALX Software Engineering, Holberton School}{Apr 2024}{San Francisco, USA}{}
\resumeSubheading{Software Engineering, Haramaya University}{June 2026}{Dire Dawa, Ethiopia}{}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Languages:} C, C++, Java, JavaScript, Python, Bash.}
\resumeItem{\textbf{Technologies:} Express.js, FastAPI, Nest.js, React.js, jQuery, Bootstrap, MongoDB, MySQL, MS SQL, Linux, Git, Redis, Docker, Kubernetes, Vim, Emacs, Photoshop, Figma, Google Ads Suite, Google Search Console, Mailchimp.}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{- \textbf{ML Tech Usage Mental Health Risk Analysis:} Analyzes behavioral data to predict mental health risks. }
\resumeItem{- \textbf{ML Spam Email Detection:} Detects spam emails using advanced machine learning models. }
\resumeItem{- \textbf{HBNB - Holberton AirBnB:} A complete AirBnB clone. }
\resumeItem{- \textbf{Mado Advertising Network:} Advertising network for Ethiopian Telegram community.}
\resumeSubHeadingListEnd

\end{document}
